Open Preprints in Ecology \& Evolution

### 2012-09-10 ms.tex
Added paragraph on using arXiv for communication
Physicists and biologists will benefit from having biologists post their
papers to arXiv, since physicists all read arXiv and they don't read
evolution journals.  Added citations for deVladar and Barton, and Frank's
series on natural selection.

>>>>

Physicists and other quantitative scientists have recently developed a
great interest in evolutionary theory, quantitative ecological theory
and epidemiological modeling.  Unfortunately this has led to a lot of
repeated work (``reinventing the wheel''; \cite{de2011contribution})
that could be avoided by better communication across disciplines.  The
near-universal adoption of preprint servers in physics provides this
vital communication channel.  We suggest that biologists reach out to
physicists and mathematicians by posting papers to arXiv: a physicist
who does not read \emph{Evolution} certainly checks arXiv at least
weekly.  This benefits both disciplines, as biologists will reach new
readers, and physicists will learn the terminology, tools and ideas
common in existing evolutionary theory.  A recent series of papers on
the theory of natural selection was posted to arXiv simultaneously
with its publication in the \emph{Journal of Evolutionary Biology}
\cite{JEB:JEB2431,JEB:JEB2498,JEB:JEB2378,JEB:JEB2373}.
